A reproducible journal article with RMarkdown&#58; A  building science template with examples for beginners based on the Elsevier journal format

### 2019-02-13 Paper/Manuscript.Rmd
Increase caption font size + add examples
For more options see here: https://stackoverflow.com/questions/37136731/set-caption-font-size-for-figures-in-yaml-header-of-rmarkdown

journal: "Building and Environment"
date: "`r Sys.Date()`"
bibliography: Bibliography.bib
output:
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
csl: advances-in-building-energy-research.csl
geometry: "left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm"
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{caption}
---

@@

# Acknowledgements
Don't forget to acknowledge the funder(s) with associated grant numbers if required. The same goes for folks who significantly assisted you with this paper but that are not authors.

# Declaration of interest
Descibe any relevant interests of the authors, particularly if there is a link to the research that is relatively uncommon and could be perceived as a conflict of interest.

>>>>

journal: "Building and Environment"
date: "`r Sys.Date()`"
bibliography: Bibliography.bib
output:
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
csl: advances-in-building-energy-research.csl
geometry: "left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm"
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage[font={small}]{caption}
---

@@

# Acknowledgements
Don't forget to acknowledge the funder(s) with associated grant numbers if required. The same goes for folks who significantly assisted you with this paper but that are not authors. Eg "Agency (grant number 12345) supported this work, with cost share provided by the Center for the Built Environment. We thank Person1 and Person2 for assistance with data collection""

# Declaration of interest
Descibe any relevant interests of the authors, particularly if there is a link to the research that is relatively uncommon and could be perceived as a conflict of interest.  Otherwise, "All authors declare no conflict of interest."
